% Thesis Acknowledgements ------------------------------------------------


%\begin{acknowledgementslong} %uncommenting this line, gives a different acknowledgements heading
\begin{acknowledgements}      %this creates the heading for the acknowlegments

\setlength{\parindent}{17.62482pt}
\setlength{\parskip}{0.0pt plus 1.0pt}

% \textbf{If you're reading this ahead of time and wondering where you are, don't worry, I'm getting to you, just writing the thesis first!}

I suppose a good place to start when thanking people in a thesis is to start with family.
To my mum, when I asked you to for help funding my doctoral degree, you said yes, instantly and without hesitation.
Considering all you have done and sacrificed for me throughout my life, you agreeing to help me was another act of kindness that I can barely repay (trust me, I've done the maths).
You've been there for me, every step of the way, I could not ask for a more wonderful mum, and I hope I can make you proud.
Thank you to the rest of my family, in particular my dad, Cress, Olivia, Maddy, Oscar\footnote{And Alf!}, my mum's partner (and soon to be stepdad) Neil, and my grandparents.
You are the best family anyone could ask for, and thank you for being so supportive.

I also owe a debt to my supervisor, Dr. Julian Pittard, you've gone above and beyond when it came to my supervision.
Your help and advice throughout this project has been astounding, from sending corrections to papers within a single day, to patiently explaining the finer points of the work when I was completely clueless in the first\footnote{And arguably second, third and fourth.} year.
I'm still amazed how you can rattle off a paper or three from memory when I've come into your office asking questions about a very specific part of my work.
Honestly, how do you do that? It's very impressive.

No good thesis\footnote{Though the quality of this one is debatable.} wouldn't be complete without a commitment to the authors friends.
I first met some of you on the literal first day of my undergraduate degree, it's really quite incredible how you've all tolerated my nonsense for so long.
From essentially forcing my way into Rob's house so I could cook some disastrous fried chicken, to playing \textit{Super Smash Bros.} all night long on its release day, to watching trashy movies over the internet at the height of a global pandemic, these are moments I'll treasure for the rest of my life.
In particular, those who are still in Leeds, Rob\footnote{\emph{``People can put whatever they want in footnotes, nobody reads them.''} - Dr. Rob Welch}, Matt, Kelsie, Alex and Sam; as well as those who aren't, Martin, Elliot, Caz, Andy, John and Devon.
Congratulations are also in order for Kelsie and Alex on their wedding, you did it you two!
Thank you, all of you, for filling my life with joy this past decade\footnote{And for helping to proof-read my thesis, it's a tremendous help.}.

To my partner Pruthvi, I cannot even begin to describe how unlikely it is that the two of us even met.
Two people finding and falling for each other on the more esoteric circles of the internet is like two particles colliding in the tenuous interstellar medium\ldots{}
If you'll excuse the extremely trite metaphor.
You've been loving, kind, helpful, and the most wonderful partner anyone could ask for.
I am truly blessed to know you and love you.

I would also like to thank the fantastic team at Leeds' ARC High Performance Computing department, considering the bulk of this work involves many 3D numerical simulations, my use of ARC 4's compute nodes can be described as somewhere from ``excessive'' to ``taking the piss''.
I also apologise for that one time I ran my simulations on the login nodes for multiple days, I swear it was an accident.

I would also like to thank two figures from my formative years for inspiring me.
The first is my 9\ts{th} year Physics teacher, Isobel Why, who re-kindled my interest in the field, she was the finest teacher I ever had, turning me from an underachieving student to a keen and committed aspiring physicist.
She truly had faith in all of her students, and pushed them far beyond what they thought themselves capable of.
Whilst she left teaching shortly after that year, I will never forget her impact on my life and my work.
Another is quite indirect, but still important, I would be amiss to thank Winchell ``Nyrath'' Chung, curator of the website \footlink{Atomic Rockets}{http://projectrho.com/public\_html/rocket/}.
Winchell's work is perhaps one of the most complete and exhaustive archive of real life and fictional rocketry and space exploration resources - whilst I haven't called on his work much during my career in astrophysics, I pored over this website when I was younger (perhaps reading it more thoroughly than any of my course textbooks).
It was fascinating, insightful and inspiring not only to me, but thousands of readers; the number of projects, from hard SFF novellas to honest-to-goodness research proposals hinge on his tireless efforts to catalogue humankind's exploration of space in both reality and fiction.
I learned of his cancer diagnosis whilst writing this thesis, and it cut me to my core.
Without his work I don't think I would have turned a fascination with space into a lifelong passion.
Thank you so much, both of you, you may not realise it, you may not ever read this, but you changed my life.

% This one might need to be moved, considering the above paragraph 
Finally, I would like to thank Leandro Panizzon and his wife, Margarita, though Methylphenidate was originally synthesised by him to treat her low blood pressure, it also works quite well for dragging my attention-deficit disorder riddled brain through this PhD.

\end{acknowledgements}
%\end{acknowledgmentslong}

% ------------------------------------------------------------------------

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../thesis"
%%% End: 
