\begin{Common_Symbols}

List of common symbols, if symbol requires a derivation, the appropriate equation within this thesis will be referenced. If the symbol is a constant, the value in CGS units will be provided. 

\begin{longtable}[c]{lll}
  \hline
  \endhead
  \hline
  \endfoot


  % Include symbols requiring derivation here, try and sort them by alphabet/greek alphabet
  % Perhaps could also be ordered by chapter/function?

  % Alphabetical symbols

  \multicolumn{3}{c}{\textbf{Variables}} \\
  \hline

  $a$ & Grain radius & Section \ref{sec:dust} \\
  $C$ & Courant-Friedrichs-Lewy condition & Eq. \ref{eq:cfl} \\ 
  $f$ & Wind shock fraction & Eq. \ref{eq:windshockfraction} \\
  $h_e$ & Electron transparency & Section \ref{sec:wcrcooling} \\
  $H$ & Grain heating rate & Eq. \ref{eq:grainheatingratech3} \\
  $H\rms{coll}$ & Grain heating rate due to atoms and ions & Eq. \ref{eq:grainheatingratech3} \\
  $H\rms{el}$ & Grain heating rate due to electrons & Eq. \ref{eq:grainheatingratech3} \\
  $i$ & Inclination & Section \ref{sec:importantwcd} \\
  $\mathcal{L}$ & Cooling rate per unit volume & Eq. \ref{eq:energylossrate} \\ 
  $\lumin_\star$ & Stellar luminosity & Section \ref{sec:evolvedstars} \\
  $\mass_\star$ & Stellar mass & Section \ref{sec:evolvedstars} \\
  $\mdot$ & Mass loss rate & Section \ref{sec:stellarwinds} \\
  $t\rms{cool}$ & Cooling timescale & Eq. \ref{eq:taucool} \\
  $t\rms{esc}$ & Escape timescale & Eq. \ref{eq:tauesc} \\
  $v_\infty$ & Wind terminal velocity & Section \ref{sec:stellarwinds} \\
  $z$ & Dust-to-gas mass ratio & Section \ref{sec:dustimplementation} \\

  % Greek symbols

  $\beta$ & Electron ion ratio & Section \ref{sec:gas-dust-cooling} \\
  $\eta$ & Wind momentum ratio  & Eq. \ref{eq:etach2} \\
  
  $\Lambda(T)$ & Plasma Cooling function & Section \ref{sec:gas-dust-cooling} \\

  $\xi$ & Grain sticking efficiency & Eq. \ref{eq:dustgrowthradiuschange} \\

  $\theta\rms{c}$ & WCR conic opening angle & Eq. \ref{eq:conic} \\
  
  $\tau_\text{KH}$ & Kelvin-Helmholtz timescale & Eq. \ref{eq:khtime} \\
  $\tau_\text{ff}$ & Free-fall timescale & Eq. \ref{eq:fftime} \\

  $\mu$ & Mean molecular mass & Eq. \ref{eq:idealgasch2} \\

  $\kappa$ & Sub-timestep fraction & Section \ref{sec:cooling-implementation} \\

  $\Phi$ & Orbital phase & Section \ref{sec:orbitsolver} \\

  $\chi$ & Cooling parameter  & Eq. \ref{eq:coolingparameter} \\

  $\gamma$ & Ratio of specific heats & Eq. \ref{eq:ch3remapzones} \\

  % Include Units from here
  \hline
  \multicolumn{3}{c}{\textbf{Subscripts \& Superscripts}} \\
  \hline

  $x\rms{WR}$   & Wolf-Rayet, synonymous with primary star & \\
  $x\rms{OB}$   & OB type, synonymous with secondary star & \\
  $x\rms{w}$    & Either wind & \\
  $x\rms{g}$    & Gas, typically refers to stellar wind & \\
  $x\rms{d}$    & Aggregate dust fluid & \\
  $x\rms{gr}$   & Single dust grain & \\
  $x\rms{H}$    & Hydrogen & \\
  $x_e$         & Electron & \\
  $x\rms{u}$    & Upper, typically the closest bin $>$ value in a lookup table & \\
  $x\rms{l}$    & Lower, typically the closest bin $<$ value in a lookup table & \\
  $x^\infty$    & Terminal, such as terminal velocity, $v^\infty$ & \\

  \hline
  \multicolumn{3}{c}{\textbf{Constants}} \\
  \hline

  \si{\atomicmassunit} & Atomic Mass Unit & \SI{1.661e-24}{\gram} \\

  $m\rms{H}$ & Hydrogen mass & \SI{1.00784}{\atomicmassunit} \\
  $m_e$      & Electron mass & \SI{0.00055}{\atomicmassunit} \\

  $k\rms{B}$ & Boltzmann Constant & \SI{1.381e-16}{erg.K^{-1}} \\

  $\sigma$ & Stefan-Boltzmann constant & \SI{5.670e-5}{erg.cm^{-2}.s^{-1}.K^{-4}} \\
  $c$ & Speed of light in a vacuum & \SI{2.998e+10}{cm.s^{-1}} \\

  \si{\solarmass} & Solar mass & \num{1.988e+33} \si{\gram} \\
  \si{\solarmass\per\year} & Solar mass per year & \SI{6.301e+25}{\gram\per\second} \\
  \si{\solarluminosity} & Solar luminosity & \SI{3.828e+33}{\erg\per\second} \\
  \si{\solarradius} & Solar radius & \SI{6.957e+10}{\centi\metre} \\
  \si{\au} & Astronomical Unit & \SI{1.496e+13}{\centi\metre} \\
  \si{\parsec} & Parsec & \SI{3.086e+18}{\centi\metre} \\
  ``Warm'' & Warm temperature regime & \num{1e4} -- \SI{1e5}{\kelvin}\footnote{Varies from researcher to researcher.} \\

\end{longtable}


\end{Common_Symbols}
